---
title: "Homework7"
author: "Devin Etcitty"
date: "4/18/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### STAT4205
#### dce2108


```{r message = FALSE, warning = FALSE}
library(alr4)
library(ggplot2)
library(tidyverse)
```

# Problem 9.3

```{r}
head(pipeline)
```

```{r}
plot(pipeline)
```

```{r}
labfield <- lm(Lab ~ Field, data=pipeline)
lab.line <- labfield$coefficients
lab.line
plot(pipeline[1:2])
abline(lab.line[1], lab.line[2])

```
```{r}
m1.res <- labfield$residuals

```




```{r}
fieldlab <- lm(Field ~ Lab, data=pipeline)
field.line <- fieldlab$coefficients
#field.line
plot(pipeline[2:1])
abline(field.line[1], field.line[2])

```


```{r}
n <- dim(pipeline)[1]
levs <- pf(99*c(.5), 2, n) - 1/n
with(pipeline, dataEllipse(Lab, Field),
     levels=levs - 1/n, xlim=c(-50, 200), ylim=c(-50, 120))
```



# Problem 9.8

```{r}
head(water)
```
```{r}
plot(water)
```

The problem asks:

"Draw residual plots for the mean function described in Problem 8.3.4 for the California water data, and comment on your results."

"Test for curvature as a function of fitted values"

Q: What is the model?

log(BSAMM) ~ log(APMAM) + log(APSAB) + log(APSLAKE) + log(OPBPC) + log(OPRC) + log(OPSLAKE)

```{r}
prob9.3 <- lm(log(BSAAM) ~ log(APMAM) + log(APSAB) + log(APSLAKE) + log(OPBPC) + log(OPRC) + log(OPSLAKE), data = water)
summary(prob9.3)
```


```{r}
residualPlots(prob9.3)

```

```{r}
resid <- prob9.3$residuals
fitted <- prob9.3$fitted.values

plot(fitted, resid)
```


# Problem 9.11



```{r}
head(fuel2001)
```

```{r}
plot(fuel2001)
```


```{r}
names(fuel2001)
```



### Linear Model

$$ 
E(fuel | X) = B_0 + B_1 Tax + B_2 Dlic + B_3 Income + B_4 log(miles)
$$ 

# Transform data

```{r}
fuel2001 <- transform(fuel2001,
Dlic=1000 * Drivers/Pop,
Fuel=1000 * FuelC/Pop)

```


```{r}
model9.11 <- lm( Fuel ~ Tax + Dlic + Income + log(Miles), data=fuel2001)
summary(model9.11)
```

```{r}
residualPlots(model9.11)
```



```{r}
hat_9.11 <- hatvalues(model9.11)
hat_9.11
```
```{r}

states <- c("AK", "NY", "HI", "WY", "DC")
hat_fivestates <- hat_9.11[states]
hat_fivestates
```


```{r}
fuel <- c(514.279, 374.164, 426.349, 842.792, 317.492)
ehat_fuel <- c(-163.145, -137.599, -102.409, 183.499, -49.452)
hat_fuel <- c(0.256, 0.162, 0.206, 0.084, 0.415)
states_resid <- model9.11$residuals[states]

r_hat <-   ehat_fuel / ( states_resid * sqrt(1 - hat_fuel))


r_hat
n <- 51
p_prime <- 5

t <- r_hat * ((n - p_prime - 1) / (n - p_prime - r_hat^2))^(1/2)
t


D_i <- (1/p_prime) * r_hat^2 * (hat_fuel /(1 - hat_fuel) )
names(D_i) <- states
D_i
```

```{r}
dl <- cooks.distance(model9.11)
dl

```
```{r}
r <- rstudent(model9.11)
r
```


```{r}
r.newModel <- r[states]
dl.newModel <- dl[states]



n <- 51
p_prime <- 5

t <- r.newModel * ((n - p_prime - 1) / (n - p_prime - r.newModel^2))^(1/2)
t
```

```{r}
r.newModel
```

```{r}
dl.newModel
```
```{r}

p.new <- 2*pt(-abs(t),df=n-1)

p.adjust(p.new, method = "bonferroni")
```

```{r}
outlierTest(model9.11)
```

Wyoming has the largest influence on the regression


```{r}
influenceIndexPlot(model9.11)
```



#Extra Practice Problems
==========

# Problem 9.1

```{r}
head(Rpdata)
```

```{r}
pairs(Rpdata)
```

The variables next to each other seem strongly correlated, except with x1 and y. x1 neighbors is x2. 


```{r}
ggplot(Rpdata, aes(x1, y)) +
  geom_point() +
  geom_smooth(method=lm)
```


```{r}
ggplot(Rpdata, aes(x2, y)) +
  geom_point() +
  geom_smooth(method=lm)
```



```{r}
ggplot(Rpdata, aes(x3, y)) +
  geom_point() +
  geom_smooth(method=lm)
```


```{r}
ggplot(Rpdata, aes(x4, y)) +
  geom_point() +
  geom_smooth(method=lm)
```


```{r}
ggplot(Rpdata, aes(x5, y)) +
  geom_point() +
  geom_smooth(method=lm)
```

```{r}
ggplot(Rpdata, aes(x6, y)) +
  geom_point() +
  geom_smooth(method=lm)
```




```{r}
pr9.1 <- lm(y ~ x1 + x2 + x3 + x4 + x5 + x6, data = Rpdata)
summary(pr9.1)
```


All the p-values are signficant. This might mean that the model is wrong.

```{r}
pr9.1.1 <- lm(x1 ~ x2,  data = Rpdata)
summary(pr9.1)
```


```{r}
pr9.1.2 <- lm(x2 ~ x1,  data = Rpdata)
summary(pr9.1.2)
```


```{r}
plot(pr9.1)
```



```{r}
resid <- pr9.1$residuals
fitted <- pr9.1$fitted.values

plot(fitted, resid)
```

```{r}
residualPlots()
```

