---
title: "Homework 3"
author: "Devin Etcitty"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### STAT4205
#### dce2108



```{r message = FALSE, warning = FALSE}
library(alr4)
library(tidyverse)
```

#### Problem 3.3
<!--- Berkeley Guidance Study --->
```{r}
plot(BGSgirls)
```
```{r}
matrix_girls <- BGSgirls %>%
  select(HT2, HT9, WT2, WT9, ST9, BMI18)
  
```

```{r}
plot(matrix_girls)
```



With BMI18 as a reponse variable, it seems to have a horizontal linear relationship with the 5 other variables.
However, the 5 other variables have an increasing linear relationship with one another. 

```{r}
round(cor(matrix_girls), 4)
```

For sample corrlations, BMI18 has low correlation coefficients with the other 5 variables (<0.55). The other variables have relatively high correlation correfficients, between the ranges of 0.4 and 0.73.


```{r}
round(var(matrix_girls), 4)

```

```{r}
round(cov(matrix_girls), 4)
```


```{r}
wt9 <- lm(BMI18 ~ WT9, data=matrix_girls)
summary(wt9)
```

```{r}
avPlots(wt9, id.n=0)
```


```{r}
two_st <- lm(BMI18 ~ WT9 + ST9, data=matrix_girls)
summary(two_st)
```
```{r}
avPlots(two_st, id.n=0)
```
```{r}
st9 <- lm(BMI18 ~ ST9, data=matrix_girls)
summary(st9)
```

```{r}
avPlots(st9, id.n=0)
```

```{r}
ggplot(matrix_girls, aes(x=ST9, y=BMI18)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
ggplot(matrix_girls, aes(x=WT9, y=BMI18)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
ggplot(matrix_girls, aes(x=WT9, y=ST9)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

```



##### Problem 3.3.3

```{r}
model <- lm(BMI18 ~ HT2 + WT2 + HT9 + WT9 + ST9, data=matrix_girls)
summary(model)
```


```{r}
avPlots(model, id.n=0)
```

```{r}
rsqrd <- summary(model)$r.squared
sigma_hat <- sigmaHat(model)
```


```{r}
confint(model)

```

#### Problem 3.4
<!--- Mean function --->

#### Problem 3.5
<!--- Regression mean function: Double variable --->



#### Problem 3.6
<!--- Correlation Matrix --->
```{r}
attach(water)

detach(water)
```


#### Problem 4.1
<!--- Orthogonal polynomials --->
```{r}
attach(BGSgirls)

detach(BGSgirls)
```



#### Problem 4.9



